DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
implemented Alessadro's suggestions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} \textcolor{red}{[fix ref]} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

@@

\textcolor{red}{[Pls update CAV reference with details from proof of article just received from Springer. ]}

>>>>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

@@
